The imprint of global magma oceans on exoplanet demographics

### 2023-03-09 src/tex/ms.tex
explain planet sample
Added details for generating the synthetic planet sample.

We find that retrievals from radius measurements alone require high fractions of greenhouse climate-bearing planets to achieve an accurate constraint on $S_\mathrm{thresh}$:
Dilution factors $f_\mathrm{rgh} \gtrsim 0.5$ yield posterior probability distributions that are condensed at the order of magnitude of the true value; accurate constraints to within $\pm 0.25\,\mathrm{dex}$ of the truth are reached only from $f_\mathrm{rgh} \approx 0.8$.

In contrast, if planet masses are available and the hypothesis test is conducted in bulk density space, useful constraints emerge already from about $f_\mathrm{rgh} \approx 0.35$.
Accuracy and precision of the retrievals are improved.

A sample containing only planets around M~dwarf yields a very similar performance, which is because these planets contribute most to the statistical power of the retrieval.

>>>>

Accurate retrievals from radius measurements alone require high fractions of greenhouse climate-bearing planets to achieve an accurate constraint on $S_\mathrm{thresh}$.
If, on the other hand, a follow-up campaign adds planetary mass estimates and we fit the signal in bulk density space, useful constraints are possible under more pessimistic conditions.
A sample containing only planets around M~dwarf yields a performance comparable to that of the overall sample.
